---
title: "simpleRegress"
author: "Diego Martinez"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

$H_0$: There is no different (in length) between different bear body parts

$H_A$: There is a difference (in length) between different bear body parts.

# Methods 

This is a numerical~numerical case so I will be using my helper file to use the correct graphical, numerical, and inferential methods. Since length is numerical, and we're comparing between 2 lengths to see which has the highest Adjusted- R squared. 



## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```


This data chart allows me to see the different body parts that I have to compare & shows me various amounts of numerical data stating the size of a certain body part. 

# Graphical Results 

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
```
 
I can tell that this graph is linear and positive. This graph describes the relationship between length and the bear neck. We can see that the higher the neck value is, the higher the length is too. Thus, it's a positive relationship between the two. 


# Numerical 


### now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

We can see that the predicted values are listed below. With a neck size of 17, the predicted length is 52.8. With a neck size of 22, the predicted length is 61. With a neck size of 26, the predicted length is 67.6. 


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


# Inferential Results 

```{r}
chesty <- lm(LENGTH~CHEST, data=bears)
plot(LENGTH~CHEST, data = bears)
abline(chesty)
summary.lm(chesty)
```
   
The adjusted R-square for this model (CHEST) is .79; the model for NECK had an adjusted R-square of .75. So far the best model is the one based on CHEST since it's adjusted R-square is of higher value. 
              
```{r}
new <- data.frame(CHEST=c(17,22,26))
predict(chesty,new)
predict(chesty,new,se.fit=TRUE) 
```

We can see that the predicted values are listed below. With a chest size of 17, the predicted length is 39.6. With a chest size of 22, the predicted length is 44.7. With a chest size of 26, the predicted length is 48.8. 



```{r}
Hi <- lm(LENGTH~HEADLEN, data=bears)
plot(LENGTH~HEADLEN, data = bears)
abline(Hi)
summary.lm(Hi)
```

The adjusted R-square for this model (HEADLEN) is .84; the model for AGE had an adjusted R-square of .84. So far, AGE & HEADLEN are tied for the highest adjusted R-squared value. 

For AGE: 

The adjusted R-square for this model (AGE) is .84; the model for NECK had an adjusted R-square of .75. So far, this is our highest value out of all the adjusted R-squared since .84 is greater than .75. 

# Conclusion


I have tried all of them. The highest one by far is head length. In conclusion, the one with the highest Adjusted R-squared is head length. HEADLEN has the highest value out of all of them. I tried all the values by changing the name and body part in the same code until the highest number appeared.



