---
title: "simpleRegress"
author: "Diego Martinez"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

$H_0$: There is no difference (in length) between different bear body parts: all body parts have the same adjusted R-squared value. 

$H_A$: There is a difference (in length) between different bear body parts: not all body parts have the same adjusted R-squared value.

# Methods 

This is a numerical~numerical case so I will be using my helper file to use the correct graphical, numerical, and inferential methods. Since length is numerical, and we're comparing between 2 lengths to see which has the highest Adjusted- R squared. 



## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```


This data chart allows me to see the different body parts that I have to compare & shows me various amounts of numerical data stating the size of a certain body part. 

# Graphical Results 

## Model LENGTH ~ NECK  this is an example  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
```
 
I can tell that this graph is linear and positive. This graph describes the relationship between length and the bear neck. We can see that the higher the neck value is, the higher the length is too. Thus, it's a positive relationship between the two. 


# Numerical 


### now predict the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

We can see that the predicted values are listed below. With a neck size of 17, the predicted length is 52.8. With a neck size of 22, the predicted length is 61. With a neck size of 26, the predicted length is 67.6. 


## Surely there is another variable that can better predict LENGTH than NECK. Find one and compare its performance to that of neck by it value of Adjusted-Rsquared (bigger is better).


# Inferential Results 

```{r}
chesty <- lm(LENGTH~CHEST, data=bears)
plot(LENGTH~CHEST, data = bears)
abline(chesty)
summary.lm(chesty)
```
   
The adjusted R-square for this model (CHEST) is .79; the model for NECK had an adjusted R-square of .75. So far, the best model is CHEST since it's adjusted R-squared is of higher value. 
              
```{r}
new <- data.frame(CHEST=c(17,22,26))
predict(chesty,new)
predict(chesty,new,se.fit=TRUE) 
```

We can see that the predicted values are listed below. With a chest size of 17, the predicted length is 39.6. With a chest size of 22, the predicted length is 44.7. With a chest size of 26, the predicted length is 48.8. 



```{r}
Hi <- lm(LENGTH~HEADLEN, data=bears)
plot(LENGTH~HEADLEN, data = bears)
abline(Hi)
summary.lm(Hi)
```

The adjusted R-square for this model (HEADLEN) is .84; the model for AGE has an adjusted R-square of .84 too. So far, AGE & HEADLEN are tied for the highest adjusted R-squared value.The model for NECK had an adjusted R-squared value of .75: .84 is the highest value out of all the adjusted R-squared values since it's greater than every other value. 

# Conclusion

I have seen all the adjusted R-squared values. The highest two by far is head length & age. In conclusion, the two with the highest Adjusted R-squared is head length & age.  I tried all the values by changing the name and body part in the same code until the highest number appeared. After writing down all the adjusted R-squared values, we have a tie. Head length and age have an adjusted R-squared value of .84. No other body parts had a higher value. We can reject the null hypothesis since not all body parts had the same adjusted R-squared value. 



